### 2021-05-09 papers/SYRCoSE/regmachine-eventstruct.tex
more grammar

The rules of operational semantics constructing 
the event structure are presented in~\cref{fig:eventstruct-sem}.
The first auxiliary rule \ESAddEventRule adds a new event, sets its 
label, $\lPO$ and $\lRF$ predecessors. 
The \ESIdleRule handles the case when a thread of 
the register machine performs an internal step 
without any side effect. 
It chooses an event~$e$ together with 
the thread state~$s$ corresponding to it
and performs one step reduction to a new state~$s'$.
It then updates the mapping of events to thread states.   
The last three rules \ESStoreRule, \ESLoadRule, and \ESLoadBotRule
correspond to store and load performed by some thread.  
Similarly to \ESIdleRule, an event $e_{\lPO}$ is selected
and one reduction is performed from the corresponding thread state~$s$.
Unlike the \ESIdleRule case, however, a new event~$e$ is also generated.
In case of \ESLoadRule additionally an event~$e_{\lRF}$ is selected,
such that it has a write label matching the read label of the new event.    
The rule \ESLoadBotRule corresponds to a case when load 
is performed ``too early'', before any write to the given location is available.

@@

We sketch the proof below\footnote{
One can also find mechanized proof in our \coq development.
}.

>>>>

The rules of operational semantics constructing 
the event structure are presented in~\cref{fig:eventstruct-sem}.
The first auxiliary rule \ESAddEventRule adds a new event, sets its 
label, $\lPO$ and $\lRF$ predecessors. 
The \ESIdleRule handles the case when a thread of 
the register machine performs an internal step 
without any side effect. 
It chooses an event~$e$ together with 
the thread state~$s$ corresponding to it
and performs one step reduction to a new state~$s'$.
It then updates the mapping of events to thread states.   
The last three rules \ESStoreRule, \ESLoadRule, and \ESLoadBotRule
correspond to store and load performed by some thread.  
Similarly to \ESIdleRule, an event $e_{\lPO}$ is selected
and one reduction is performed from the corresponding thread state~$s$.
Unlike the \ESIdleRule case, however, a new event~$e$ is also generated.
In the case of \ESLoadRule, additionally, an event~$e_{\lRF}$ is selected,
such that it has a write label matching the read label of the new event.    
The rule \ESLoadBotRule corresponds to a case when load 
is performed ``too early'', before any write to the given location is available.

@@

We sketch the proof below\footnote{
One can also find its mechanized proof in our \coq development.
}.
